Learning Network Size while Training with ShrinkNets

### 2018-02-08 paper/ICML/evaluation.tex
First version of the final plots
Start evaluation section and add a few lines to sec 2

@@

We will start evaluating ShrinkNets with the simplest problems possible: linear
and logistic regression. As we showed, Group sparsity share similarities with
our method, this is why we will use it as baseline. We decided to focus on
multi-target linear regression because in the single target case, groups in the
Group Sparsity problem would have a size of one ($\bm{A}$ would be a vector in this
case).

@@

For each dataset we fit with different regularization parameters and measure
the error and sparsity obtained after convergence. In this context we define sparsity as the ratio of columns that have all their weight under $10^{-3}$ in absolute value. Parameters were choosed in
order to obtain the widest sparsity spectrum. Loss is normalized depending on the problem to be in the $[0, 1]$ range. We summarized the results in
\cref{sparsity_accuracy}. From our experiments it is clear that ShrinkNets can fit the data closer than Group Sparsity for the same amount of sparsity. The fact that we are able to reach very low loss demonstrate that even if our objective function is non convex, in practice it works as good or better as convex alternatives. Details about these datasets and the parameters used
are available in \cref{linear_datasets}.

@@

\subsection{Convergence and training dynamics of Neural networks}

\subsection{Hyper-optimization of ShrinkNets}

\subsection{Performance}

>>>>

\subsection{Core evaluation (CHANGE\_MY\_NAME)}

To show the versatility of our aproach we evaluate both on two very different
scenario

\subsubsection{\texttt{CIFAR10} dataset}

\gl{Cite and describe the dataset}

To solve this task we use the \texttt{VGG16} model [ref]. It is constituted of
alternating convolutional layers and \textit{MaxPool} layers interleaved by
\textit{BatchNorm} [ref] and \textit{ReLU} [ref] layers. The two last layers are
Fully connected layers separated by just a \textit{ReLU} activation function.

To turn it into a ShrinkNet we introduce \textit{Switch Layers} after each
\textit{BatchNorm} and each Fully connected (except the last one).

ShrinkNets assume that the starting size of the network is an upper bound on the
optimal size. We though that picking two times the recommended size for each
layer (that was designed for ImageNet[ref]), is a generous upper bound. For the
classification layers we use $5000$ neurons as an upper bound where the ImageNet
version uses $4096$ \gl{This is on the top of my head, need to be double checked}.

We assume no prior knowledge on the optimal batch size, learning rate,
$\lambda$ or weight decay ($\lambda_2$). This is why, we randomly sample them
from a range of reasonable values (\gl{should we make them explicit ?}).
For each of the models we trained, we pick the epoch with the best validation
accuracy and report the corresponding testing accuracy. For each model, we also
measure the total size, in number of floating point parameters, excluding the
\textit{Switch Layers} because as we saw in section \gl{REFERENCE\_ME}, we can
get rid of them when training is done.

We want to compare against classical (\textit{Static}) networks. The number of
parameters that control the size is large: 13 for the size of convolutional
layers and $2$ for the fully connected ones. Without Shrinknets to help and fuse
all these parameters in a single $\lambda$ it is infeasible to sample reasonably
well a search space of that size. This is why we have to rely on the very well
known heuristic that the original VGG architecture (and many CNNs) \gl{try to
  find the paper that introduces this heuristic}. For \textit{Static Networks}
we sample the size between $0.1$ and $2$ times the size optimized for ImageNet.
We report the same numbers as we did for \textit{ShrinkNets} and we compare the
two distributions of models we obtain on the first plot of \cref{figure_CIFAR10}.

\subsubsection{\texttt{COVERTYPE} dataset}

We followed the same procedure 
\gl{Cite and describe the dataset}

We try to fit

\subsection{Benefits of smaller sizes}

We showed in the previous section that \textit{ShrinkNets} were able to find
more or at least as efficient as \textit{Static Networks}. In this experiment we
want to determine the perf

@@

As we showed, Group sparsity share similarities with our method, and we claim
that ShrinkNets are a relaxation of group sparsity.  In this experiment we want
to compare the two aproaches.  We decided to focus on multi-target linear
regression because in the single target case, groups in the Group Sparsity
problem would have a size of one ($\bm{A}$ would be a vector in this case).

@@

For each dataset we fit with different regularization parameters and measure
the error and sparsity obtained after convergence. In this context we define
sparsity as the ratio of columns that have all their weight under $10^{-3}$ in
absolute value. Regularization parameters were choosed in order to obtain the
widest sparsity spectrum. Loss is normalized depending on the problem to be in
the $[0, 1]$ range. We summarized the results in \cref{sparsity_accuracy}. From
our experiments it is clear that ShrinkNets can fit the data closer than Group
Sparsity for the same amount of sparsity. The fact that we are able to reach
very low loss demonstrate that even if our objective function is non convex, in
practice it works as good or better as convex alternatives. Details about these
datasets and the parameters used are available in \cref{linear_datasets}.

@@

\begin{figure}
\begin{center}
\includegraphics[width=\columnwidth]{CIFAR10_VGG_summary}
\vspace*{-5mm}
\caption{\label{figure_CIFAR10} Summary of the result of random
search over the hyper-parameters the \texttt{CIFAR10} dataset}
\end{center}
\vspace*{-4mm}
\end{figure}

\begin{figure}
\begin{center}
\includegraphics[width=\columnwidth]{COVER_FC_summary}
\vspace*{-5mm}
\caption{COVER}
\end{center}
\vspace*{-4mm}
\end{figure}
